### 2021-05-03 newvariant.tex
funding done

B.M.B. was supported by Natural Sciences and Engineering Research Council of Canada (NSERC). 
J.S.W. was supported by National Science Foundation (2032082).
% J.D. was supported by Canadian Institutes of Health Research (CIHR).
The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

>>>>

B.M.B. was supported by the Natural Sciences and Engineering Research Council of Canada 
J.D. was supported by the Canadian Institutes of Health Research, 
the The Natural Sciences and Engineering Research Council of Canada, 
and the Michael G. DeGroote Institute for Infectious Disease Research.
J.S.W. was supported by the National Science Foundation (2032082).
The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
